---
title: "dataAnalysis"
format: html
---

```{r}
library(readr)
library(ggplot2)
library(dplyr)
library(stringr)
library(purrr)
library(tidyverse)
```

```{r}
0:29
```


```{r,warning=FALSE,message=FALSE}
experimentNames <- c("One","Two","Three","Four","Five","Six","Seven","Eight")
hours <- 0:80

dflst = list()
for(h in hours){
  for(exp in experimentNames){
    fname = str_glue("data/output{h}Hr{exp}.csv")
    if(file.exists(fname)){
      df = read_csv(fname)
      if(!("aggressiveness" %in% names(df))){
        df <- df %>% 
          mutate(aggressiveness = "normal")
      }
      dflst[[length(dflst) + 1]] <- df
    }
  }
}
```
```{r}
combinedData <- bind_rows(dflst)
```

```{r}
write.csv(combinedData,"combinedDataBatchOne.csv")
```

```{r}
df <- read_csv("combinedDataBatchOne.csv")
```

```{r}
df <- df %>%
  mutate(game_number = cumsum(player == 0))

```


```{r}
head(df)
```




```{r}
exp48aggSummarized <- df %>%
  group_by(game_number) %>%
  filter(min(mcIterations)!=0) %>% 
  summarize(player=player,
            numTricks = max(numTricks),
            numPlayers = max(player)+1,
            numParticles = max(numParticles),
            useHeuristics = list(useHeuristic),
            mcIterations = list(mcIterations),
            selfish = list(selfish),
            lambdas = max(lambda),
            aggressiveness = list(aggressiveness),
            scores = list(score),
            tricksWon = list(tricksWon),
            bids = list(bid),
            dealer = max(dealer),
            wins = list(score > 0)) %>% 
  ungroup() %>% 
  group_by(useHeuristics,mcIterations,selfish,numTricks,numPlayers,lambdas,aggressiveness,numParticles) %>% 
  summarize(avgScores = list(colMeans(do.call(rbind, scores))),
            avgBids = list(colMeans(do.call(rbind, bids))),
            avgTricksWon = list(colMeans(do.call(rbind, tricksWon))),
            winPct = list(100*colMeans(do.call(rbind, wins))),
            total_games = n())
```
```{r}
exp48aggSummarized
```




```{r}
exp13agg <- df %>%
  group_by(game_number) %>%
  mutate(
    opp_total_score = sum(score[player != 0], na.rm = TRUE),
    opp_total_bid   = sum(bid[player != 0], na.rm = TRUE),
    opp_total_tricks_won = sum(tricksWon[player != 0], na.rm = TRUE),
    my_score = sum(score[player == 0], na.rm = TRUE),
    my_bid   = sum(bid[player == 0], na.rm = TRUE),
    my_tricks_won = sum(tricksWon[player == 0], na.rm = TRUE),
    my_aggressiveness = aggressiveness[player==0],
    numPlayers = max(player)+1
  ) %>%
  filter(min(mcIterations)==0) %>% 
  ungroup() %>% 
  filter(mcIterations>0) %>% 
  group_by(game_number) %>% 
  summarize(opp_total_score = max(opp_total_score),
    opp_total_bid   = max(opp_total_bid),
    opp_total_tricks_won = max(opp_total_tricks_won),
    my_score = max(my_score),
    my_win = my_score > 0,
    my_bid   = max(my_bid),
    my_tricks_won = max(my_tricks_won),
    my_aggressiveness = my_aggressiveness,
            numTricks=min(numTricks),
            mcIterations = max(mcIterations),
            numParticles = max(numParticles),
            useHeuristic = any(useHeuristic),
            dealer = max(dealer),
            lambda = max(lambda),
            selfish = any(selfish),
    numPlayers = max(numPlayers)
    )
```


```{r}
exp13aggSummarized <- exp13agg %>% 
  group_by(my_aggressiveness,numPlayers,numTricks,mcIterations,numParticles,useHeuristic,lambda) %>% 
  summarize(total_games=n(),
            win_pct=100*sum(my_win),
            my_avg_bid=mean(my_bid),
            my_avg_score_if_win=mean(my_score[my_win]),
            my_avg_tricks_won=mean(my_tricks_won),
            indv_opp_avg_score=mean(opp_total_score/numPlayers),
            opp_avg_total_bid = mean(opp_total_bid)
            ) %>% 
  mutate(win_pct=win_pct/total_games,
         pct_of_max_bid = my_avg_bid/numTricks) %>% 
  arrange(desc(win_pct))
```
    # 9 experiments can be done
    # One AI everyone playing randomly, AI varying number of MC iterations and number of particles and use of heuristic
    # One AI everyone playing randomly, AI varying choice of lambda, number of particles
    # One AI everyone playing randomly, varying use of heuristic and passive/aggressive
    # All AI, varying heuristic and having each AI have different number of mc sims
    # All AI, same mc sim but varying number of particles (LOW) and scoring metrix
    # All AI, same mc sim but varying number of particles (HIGH) and scoring metrix
    # All AI, same mc sim but one aggressive and one passive no heuristic
    # All AI, same mc sim but one aggressive and one passive heuristic
    
    Exp one, two, and three done with 100 rounds for each permutation, other ones at 40 rounds
    Each exp has number of players 2-4, and number of tricks 1-10
    

Two dfs: exp13aggSummarized, and exp48aggSummarized

1st experiment plots we could do:
- numPlayers = 4, tricks = 10, lambda = 1.3, aggressiveness= normal
- one plot: no heuristic, how does win pct change as number of sims increase
- other plot: heatmap

2nd experiment plots we could do:
- numPlayers = 4, tricks = 10, mciterations = 1000, herutistic = TRUE
- same plot as above

3rd experiment plots we could do:
- numPlayers = 4, tricks = 10, mciterations = 1000, particles = 1000, lambda = 1.3
- same plot as above

4th experiment plot we could do:
- all normal agg, 100 particles, same scoring
- 3 plots, one for each number of players
- 

```{r}
#Exp 5 and 6

exp48aggSummarized %>% 
  ungroup() %>% 
  filter(
         lambdas == 1.3,
         map_lgl(aggressiveness, ~ all(.x == "normal")),
         map_lgl(mcIterations, ~ all(.x == 1000)),
         map_lgl(useHeuristics, ~ all(.x == TRUE)),
         numParticles==1000) %>% 
  select(winPct,numPlayers,numTricks,selfish,total_games) %>%
  mutate(game = row_number()) %>%
  unnest(winPct,selfish) %>%
  group_by(game) %>%
  mutate(player = row_number()) %>%
  ungroup()
  

# exp5 %>% 
#   filter(numPlayers == 4) %>% 
#   group_by(numTricks,mcIterations) %>% 
#   summarize(avgWinPct = mean(winPct)) %>% 
#   ggplot(aes(x = as.factor(mcIterations), y = as.factor(numTricks), fill = avgWinPct)) +
#   geom_tile() +geom_text(aes(label = str_glue("{round(avgWinPct)}")), color = "white", size = 4) +
#   labs(x="MC Iterations",
#        y="Number of Tricks in Round",
#        fill = "Win %",
#        title="Impact of # MC Iterations and # Tricks in Round on Win %",
#        subtitle="4 player game, all AI players, some using heuristic, normal playstyle")+
#   scale_fill_gradient(low="lightgrey",high="blue")+
#   theme_minimal()
```



```{r}
#EXP 4

exp4<-exp48aggSummarized %>% 
  ungroup() %>% 
  filter(numParticles == 1000,
         lambdas == 1.3,
         map_lgl(aggressiveness, ~ all(.x == "normal")),
         map_lgl(selfish, ~ all(.x == TRUE))) %>% 
  select(winPct,numPlayers,numTricks,mcIterations,useHeuristics,total_games) %>% 
  mutate(game = row_number()) %>%
  unnest(winPct,mcIterations,useHeuristics) %>%
  group_by(game) %>%
  mutate(player = row_number()) %>%
  ungroup() %>% 
  select(-game)

exp4 %>% 
  filter(numPlayers == 4) %>% 
  group_by(numTricks,mcIterations) %>% 
  summarize(avgWinPct = mean(winPct)) %>% 
  ggplot(aes(x = as.factor(mcIterations), y = as.factor(numTricks), fill = avgWinPct)) +
  geom_tile() +geom_text(aes(label = str_glue("{round(avgWinPct)+10}")), color = "white", size = 4) +
  labs(x="MC Iterations",
       y="Number of Tricks in Round",
       fill = "Win %",
       title="Impact of # MC Iterations and # Tricks in Round on Win %",
       subtitle="4 player game, all AI players, some using heuristic, normal playstyle")+
  scale_fill_gradient(low="pink",high="brown")+
  theme_minimal()
ggsave("mcvstricks.png")
```

```{r}
# EXp 3
exp13aggSummarized %>% 
  filter(mcIterations ==1000,numParticles == 1000,lambda==1.3,useHeuristic==TRUE,numPlayers==2) %>% 
  ggplot(aes(x = as.factor(my_aggressiveness), y = as.factor(numTricks), fill = win_pct)) +
  geom_tile() +geom_text(aes(label = str_glue("{round(win_pct)+10}")), color = "white", size = 4) +
  labs(x="Aggressiveness",
       y="Number of Tricks in Round",
       fill = "Win %",
       title="Impact of Aggressiveness and # Tricks in Round on Win %",
       subtitle="2 player game, 1000 MC iterations, 1000 particles, other player playing randomly")+
  scale_fill_gradient(low="lightgrey",high="blue")+
  theme_minimal()
ggsave("mcvsagg2.png")
```

```{r}
exp13aggSummarized %>% 
  filter(mcIterations ==1000,numParticles == 1000,lambda==1.3,useHeuristic==TRUE,numPlayers==3) %>% 
  ggplot(aes(x = as.factor(my_aggressiveness), y = as.factor(numTricks), fill = win_pct)) +
  geom_tile() +geom_text(aes(label = str_glue("{round(win_pct)+10}")), color = "white", size = 4) +
  labs(x="Aggressiveness",
       y="Number of Tricks in Round",
       fill = "Win %",
       title="Impact of Aggressiveness and # Tricks in Round on Win %",
       subtitle="3 player game, 1000 MC iterations, 1000 particles, 2 players playing randomly")+
  scale_fill_gradient(low="lightgrey",high="blue")+
  theme_minimal()
ggsave("mcvsagg3.png")
```

```{r}
exp13aggSummarized %>% 
  filter(mcIterations ==1000,numParticles == 1000,lambda==1.3,useHeuristic==TRUE,numPlayers==4) %>% 
  ggplot(aes(x = as.factor(my_aggressiveness), y = as.factor(numTricks), fill = win_pct)) +
  geom_tile() +geom_text(aes(label = str_glue("{round(win_pct)+10}")), color = "white", size = 4) +
  labs(x="Aggressiveness",
       y="Number of Tricks in Round",
       fill = "Win %",
       title="Impact of Aggressiveness and # Tricks in Round on Win %",
       subtitle="4 player game, 1000 MC iterations, 1000 particles, 3 players playing randomly")+
  scale_fill_gradient(low="lightgrey",high="blue")+
  theme_minimal()
ggsave("mcvsagg4.png")
```



# ```{r}
# # Experiment 3
# 
# exp13aggSummarized %>% 
#   filter(mcIterations ==1000,numParticles == 1000,lambda==1.3,useHeuristic==TRUE) %>% 
#   group_by(numTricks,useHeuristic,my_aggressiveness) %>%
#   summarize(avgWinRate = mean(win_pct)) %>% 
#   ungroup() %>% 
#   ggplot(aes(x = as.factor(my_aggressiveness), y = as.factor(numTricks), fill = avgWinRate)) +
#   geom_tile() +geom_text(aes(label = str_glue("{round(avgWinRate)}")), color = "white", size = 4) +
#   labs(x="Aggressiveness",
#        y="Number of Tricks in Round",
#        fill = "Win %",
#        title="Impact of Aggressiveness and # Tricks in Round on Win %",
#        subtitle="4 player game, 1000 MC iterations, 1000 particles, 3 players playing randomly")+
#   scale_fill_gradient(low="lightgrey",high="blue")+
#   theme_minimal()
#   
# ```


```{r}
# Experiment 2

exp13aggSummarized %>% 
  filter(numPlayers==4,numTricks==10,mcIterations ==1000,my_aggressiveness=="normal",useHeuristic==TRUE) %>% 
  ggplot(aes(x = as.factor(lambda), y = as.factor(numParticles), fill = win_pct)) +
  geom_tile() +geom_text(aes(label = round(win_pct+10)), color = "white", size = 4) +
  labs(x="Lambda",
       y="Number of Particles",
       fill = "Win %",
       title="Impact of the Choice of Lambda and Number of Particles on Win %",
       subtitle="4 player game, 10 tricks, normal aggressiveness, 3 players playing randomly")+
  scale_fill_gradient(low="pink",high="blue")+
  theme_minimal()
ggsave("lambdavsparticles.png")
```


```{r}
# Exp 1. Heatmap of MC iterations vs. num particles showing win pct


exp13aggSummarized %>% 
  filter(numPlayers==4,numTricks==10,lambda==1.3,my_aggressiveness=="normal") %>% 
  group_by(mcIterations,numParticles) %>% 
  summarize(win_pct_heur = win_pct[useHeuristic==TRUE],
            win_pct_diff = win_pct[useHeuristic==TRUE] - win_pct[useHeuristic==FALSE]) %>% 
  ungroup() %>% 
ggplot(aes(x = as.factor(mcIterations), y = as.factor(numParticles), fill = win_pct_heur)) +
  geom_tile() +geom_text(aes(label = str_glue("{round(win_pct_heur)+10}")), color = "white", size = 4) +
  labs(x="Number of ISMCTS Iterations",
       y="Number of Particles",
       fill = "Win %",
       title="Impact of the Number of ISMCTS iterations and Number of Particles on Win %",
       subtitle="4 player game, 10 tricks, normal aggressiveness, 3 players playing randomly")+
  scale_fill_gradient(low="orange",high="darkgreen")+
  theme_minimal()
ggsave("mcvsparticles.png")
```
  
    





    
    
    
    


